Study of the hadronization of charged pions

### 2019-04-16 chap5.tex
Comment some unfinished stuff

\subsection{Cross Checks}
\label{sec:XChecks}

The goal here is to check known results in order to make sure we have normalization right. This is 
especially important since discrepencies with Hayk's analysis have been found and demonstrated the 
normalization to be a tricky problem.

\subsubsection{Inclusive electron normalization}

We expect the EMC ratio to cross unity around 0.3 - 0.35 and we know precisely the target thickesses.
From these we check our inclusive normalization...

\subsubsection{Pion ratio from Hall-C}

In paper from Hall-C they present results shown in fig 20 (to reproduce here). The bin corresponds to 
1.5 < Q2 < 4 GeV2, 0.35 < xb < 0.45, 0.5 < z < 0.6 and Pt2 < 0.2. They find ratios of 0.556+-0.011 for pi+
and 0.520+-0.011 for pi-. Note that it is not a double ratio and should be affected by the EMC effect,
moreover they do not make an isospin correction which is 1.5\%.

Put my result here

\subsubsection{Pion ratio from HERMES}

>>>>

%\subsection{Cross Checks}
%\label{sec:XChecks}

%The goal here is to check known results in order to make sure we have normalization right. This is 
%especially important since discrepencies with Hayk's analysis have been found and demonstrated the 
%normalization to be a tricky problem.

%\subsubsection{Inclusive electron normalization}

%We expect the EMC ratio to cross unity around 0.3 - 0.35 and we know precisely the target thickesses.
%From these we check our inclusive normalization...

%\subsubsection{Pion ratio from Hall-C}

%In paper from Hall-C they present results shown in fig 20 (to reproduce here). The bin corresponds to 
%1.5 < Q2 < 4 GeV2, 0.35 < xb < 0.45, 0.5 < z < 0.6 and Pt2 < 0.2. They find ratios of 0.556+-0.011 for pi+
%and 0.520+-0.011 for pi-. Note that it is not a double ratio and should be affected by the EMC effect,
%moreover they do not make an isospin correction which is 1.5\%.

%Put my result here

%\subsubsection{Pion ratio from HERMES}
